Extreme heterogeneity of influenza virus infection in single cells

### 2017-09-26 paper/paper-biorxiv.tex
version for bioRxiv: remove eLife banner, added funding acknowledgments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ELIFE ARTICLE TEMPLATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE 
\documentclass[9pt,lineno]{elife}
\sloppy
% Use the onehalfspacing option for 1.5 line spacing
% Use the doublespacing option for 2.0 line spacing
% Please note that these options may affect formatting.

@@

\subsection{Computational analysis of single-cell mRNA sequencing data}
Jupyter notebooks that perform all of the computational analyses are available in Supplementary~file~\ref{suppfile:code} and at \url{https://github.com/jbloomlab/flu_single_cell} \jdbcomment{This GitHub repository will be made public upon acceptance of the manuscript. If you are a reviewer who needs access, please contact the editor.}.

@@

\section{Acknowledgments}
We thank Xiaojie Qiu for advice about use of the Monocle software package, David Bacsik and Robert Bradley for comments on the manuscript, and the Fred Hutch Genomics Core for performing the Illumina deep sequencing.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ELIFE ARTICLE TEMPLATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE 
\documentclass[9pt,lineno]{elife_biorxiv}
\sloppy
% Use the onehalfspacing option for 1.5 line spacing
% Use the doublespacing option for 2.0 line spacing
% Please note that these options may affect formatting.

@@

\subsection{Computational analysis of single-cell mRNA sequencing data}
Jupyter notebooks that perform all of the computational analyses are available in Supplementary~file~\ref{suppfile:code}.

@@

\section{Acknowledgments}
We thank Xiaojie Qiu for advice about use of the Monocle software package, David Bacsik and Robert Bradley for comments on the manuscript, and the Fred Hutch Genomics Core for performing the Illumina deep sequencing.
This work was supported by NIH grant R01GM102198 (to JDB), NIH grant R01AI127893 (to JDB), NIH grant DP2HD088158 (to CT), a Burroughs Wellcome Young Investigator in the Pathogenesis of Infectious Diseases grant (to JDB), and a W. M. Keck Foundation grant (to CT).
ABR is supported by a Damon Runyon Fellowship.
JDB is partly supported by a Faculty Scholars Award from the Howard Hughes Medical Institute and the Simons Foundation.
CT is partly supported by an Alfred P. Sloan Foundation Research Fellowship. 
The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
